Something with Objects and Names

### 2019-12-03 papers/ACL2020/experiments.tex
[ACL2020] adds tables w. confusing results :)

Note that the source dataset for defining the vocabulary (\textsl{Vocab}, i.e.,\ the overall set of considered names, i.e., the softmax layer's dimensions), and the source dataset which provides the ground truth names for the individual objects (\textsl{GTtrain}) may differ.

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|c|r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r|@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}}
		\toprule
		&   & \multicolumn{6}{c}{All Test Images ($\#$)} 
		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\	
		Model--Vocab	 
		&  GTtrain &  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR 
		&  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR\\ 
		\midrule
		FRCNN--VG2500 & VG \\
		FRCNN--VG1600 & VG & \\
		FRCNN--MN442 & VG &   \\
		\midrule \midrule
		& \multicolumn{12}{c}{Classifiers: Fine-tuning pre-trained image features on \mn}\\
		Features--Vocab & GTtrain  \\
		\midrule 
		FRCNN--VG1600--VGMN & MN &  \\
		& MN-12ep  &           \\ 
		FRCNN--VG1600--MN442 &  MN \\
		\midrule
		ResNet101--VGMN\_4ep  &   VG  \\
		ResNet101--VGMN\_8ep & VG &  \\
		ResNet101--VGMN & MN \\
		ResNet101--MN442 & VG \\
		ResNet101--MN442 & MN &\\
		\bottomrule
	\end{tabular}
	\caption{Target vocabulary in test data: MN442. Vocab denotes the dataset from which the target vocabulary for training was induced (the numbers give the size of the vocabulary). GTtrain denotes the dataset from which the ground truth labels are obtained during \textit{training}. MRR is mean reciprocal rank; J is Jaccard score.\label{tab:entrylevels}. }
\end{table*}

@@

>>>>

Note that the source dataset for defining the vocabulary (\textsl{Vocab}, i.e.,\ the overall set of considered names, i.e., the softmax layer's dimensions), and the source dataset which provides the ground truth names for the individual objects (\textsl{GTtrain}) may differ.  
\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|c|r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r|@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}}
		\toprule
		&   & \multicolumn{6}{c}{All Test Images ($\#$)} 
		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\	
		Model--Vocab	 
		&  GTtrain &  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR 
		&  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR\\ 
		\midrule
		FRCNN--MN442 & VG &            65.4 &              71.2 &                85.6 &         1.0 &             69.8 &          0.8 &             0.7 &            20.0 &              48.4 &                78.7 &         1.4 &             60.4 &          0.7 &             0.5 \\
		FRCNN--VG2500 & VG \\
		FRCNN--VG1600 & VG &            67.3 &              74.5 &                89.2 &         0.6 &             74.3 &          0.8 &             0.7 &            19.1 &              52.9 &                86.2 &         0.8 &             69.4 &          0.7 &             0.6 \\
		\midrule \midrule
		& \multicolumn{12}{c}{Classifiers: Fine-tuning pre-trained image features on \mn}\\
		Features--Vocab & GTtrain  \\
		\midrule 
		FRCNN--VG1600--VGMN & MN &            70.8 &              80.6 &                90.1 &         4.7 &             62.0 &          0.8 &             0.6 &            13.8 &              60.4 &                85.8 &         4.6 &             47.3 &          0.7 &             0.5 \\ 
		FRCNN--VG1600--MN442 &  MN \\
		\midrule
		ResNet101--VGMN & MN  &            60.9 &              68.6 &                77.9 &         4.9 &             56.4 &          0.8 &             0.6 &            13.8 &              50.2 &                73.3 &         4.7 &             42.9 &          0.6 &             0.4 \\

		ResNet101--MN442 & MN &            61.7 &              69.6 &                78.9 &         4.9 &             57.4 &          0.8 &             0.6 &            13.8 &              50.7 &                73.8 &         4.6 &             45.1 &          0.6 &             0.5 \\
		ResNet101--VGMN\_4ep  &   VG &  62.4 &              62.9 &                75.0 &         5.0 &             53.7 &          0.7 &             0.6 &            28.4 &              31.1 &                64.9 &         4.8 &             39.1 &          0.4 &             0.4 \\
		ResNet101--VGMN\_8ep & VG &            63.9 &              62.6 &                75.6 &         5.0 &             53.9 &          0.7 &             0.6 &            34.2 &              28.0 &                66.2 &         4.9 &             39.7 &          0.4 &             0.4 \\
		ResNet101--MN442 & VG  &            63.7 &              63.7 &                76.6 &         5.0 &             55.4 &          0.7 &             0.6 &            30.7 &              31.1 &                67.1 &         4.8 &             41.0 &          0.4 &             0.4 \\
		\bottomrule
	\end{tabular}
	\caption{Target vocabulary in test data: MN442. Vocab denotes the dataset from which the target vocabulary for training was induced (the numbers give the size of the vocabulary). GTtrain denotes the dataset from which the ground truth labels are obtained during \textit{training}. MRR is mean reciprocal rank; J is Jaccard score. Note that we considered all name responses in MN, including those with $\text{count}(name)<2$\label{tab:entrylevels}. }
\end{table*}

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l@{~}|rrrr}
		\toprule
		... \\
		\midrule
		Domain	 & ... \\ 
		\midrule
		All           \\
		home           \\
		food           \\
		buildings      \\
		vehicles       \\
		animals\_plants \\
		clothing       \\
		people         \\
		\bottomrule
	\end{tabular}
	\caption{RESULTS FOR SELECTED MODELS \label{tab:domains_bestmodel}}
\end{table*}

@@

\subsection{Results}
\paragraph{Overview}
Table\ \ref{tab:exp_overview_results}: \cs{Shows the overview and what MN adds without going into detail: Standard evaluation -- hit; We can additionally distinguish between correct (name alternative, see caption of Table) and clear mistake.}

\paragraph{Correct predictions}
Table\ \ref{tab:exp_details_correct}: \cs{Gives detailed results to the categories of "correct name" (but not hit): same cluster, WordNet synonym, WordNet hypernym/hyponym}\\
To look into in detail (example images): 
\begin{itemize}
	\item Compare FRCNN vs. FRCNN-finetuned (row block 1 vs. row block 2) with respect to the synonym categories (i.e., predicted name is in a synonym/synonyms\_cluster-relation to the target object) vs. same\_cluster (i.e., predicted name is in response set). 
\end{itemize}

\paragraph{Wrong predictions}
Table\ \ref{tab:exp_details_wrong}: \cs{Gives detailed results to the categories of predicted name\ $\hat{n}$ is incorrect: WordNet co-hyponyms,  other object (inadequacy types: visual, linguistic, bounding box, other (types other+None), $\text{count}(\hat{n})<2$, error (just wrong+unkn(not found in WordNet))}

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|l|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
		\toprule
		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
	\toprule
	Model--Vocab	& GTtrain  
	&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
	\midrule
	FRCNN--VG1600 & VG           &         0.75 &                  0.14 &                    0.11 &         0.54 &                  0.30 &                    0.16 \\
	RCNN--MN442 & VG &         0.71 &                  0.13 &                    0.15 &         0.48 &                  0.28 &                    0.24 \\
	\midrule \midrule
	FRCNN--VG1600--VGMN & MN &         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
	\midrule
	ResNet101--MN442 & MN & 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
	ResNet101--VG1600 & MN &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
	ResNet101--VG1600 & VG &         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
	ResNet101--MN442 & VG &         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
	\bottomrule
\end{tabular}
\caption{Break-down of the results: Categorization of the predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf. standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake). \label{tab:exp_overview_results}}
\end{table*}

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{llr@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
		\toprule
		& & \multicolumn{6}{c}{All Test Images ($\#$)} 
		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\
		\toprule
		& &  same &  syn. &  syn. &  hyper. &  hypo. &  hypo. &  same &  syn. &  syn. &  hyper. &  hypo. &  hypo. \\
		& 	&  cluster &  & cluster & & & cluster 
			& cluster  &  & cluster & & & cluster \\
		\midrule
		FRCNN--VG1600 & VG             &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
		RCNN--MN442 & VG &                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
		\midrule \midrule
		FRCNN--VG1600--VGMN & MN &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
		\midrule
		ResNet101--VGMN & MN &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
		ResNet101--MN442 & MN & 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
		ResNet101--VGMN & VG &                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
		ResNet101--MN442 & VG &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\		
		\bottomrule
	\end{tabular}

	\caption{Break-down of the results for the \textit{correct} name predictions. \textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name. \textit{hyponym\_cl}: $\hat{n}$ is a hyponym of any of the valid names (cluster). \textit{Synonym} and \textit{synonym\_cl} are analogous. \label{tab:exp_details_correct}}
\end{table*}

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{ll|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
		\toprule
		&& \multicolumn{7}{c}{All Test Images ($\#$)} 
		& \multicolumn{7}{c}{VG$\neq$MN Images ($\#$)}\\
		\toprule
		Model--Vocab & GTtrain  
		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low 
		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low \\
		& & hypo. & (vis. &  ling. &  box &  other)   & & count 
		&  hypo. & (vis. &  ling. &  box &  other) &   & count     \\

	\midrule
	FRCNN--VG1600 & VG     &                 0.06 
		&            0.02 &                 0.0 &                  0.16 &           0.06 &           0.49 &             0.20 &                 0.03 &            0.05 &                 0.0 &                  0.16 &           0.13 &           0.50 &             0.13 \\
	FRCNN--MN442 & VG       &                 0.06 
		&            0.01 &                 0.0 &                  0.15 &           0.06 &           0.60 &             0.13 &                 0.02 &            0.02 &                 0.0 &                  0.13 &           0.11 &           0.60 &             0.11 \\
	\midrule \midrule
	FRCNN--VG1600--VGMN & MN &                 0.14 
		&            0.01 &                 0.0 &                  0.12 &           0.05 &           0.50 &             0.17 &                 0.11 &            0.03 &                 0.0 &                  0.16 &           0.11 &           0.50 &             0.11 \\
	\midrule
		ResNet101--VGMN & MN		&                 0.11 &             0.0 &                 0.0 &                  0.12 &           0.01 &           0.64 &             0.11 &                 0.03 &             0.0 &                 0.0 &                  0.12 &           0.05 &           0.69 &             0.10 \\
	ResNet101--MN442 & MN &                 0.09 
		&             0.0 &                 0.0 &                  0.13 &           0.02 &           0.63 &             0.13 &                 0.05 &             0.0 &                 0.0 &                  0.15 &           0.07 &           0.62 &             0.12 \\
	ResNet101--VGMN & VG &                 0.10 
			&             0.0 &                 0.0 &                  0.06 &           0.02 
			&           0.69 &             0.12 
		&  0.04 
			&             0.0 &                 0.0 &                  0.03 &           0.06 
			&           0.67 &             0.20 \\ 
	ResNet101--MN442 & VG &                 0.08 &             0.0 &                 0.0 &                  0.07 &           0.03 &           0.69 &             0.13 &                 0.01 &             0.0 &                 0.0 &                  0.06 &           0.08 &           0.62 &             0.23 \\
	\bottomrule
\end{tabular}
\caption{Break-down of the results for the \textit{wrong} name predictions.  \label{tab:exp_details_wrong}}
\end{table*}
